---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vbdata

<!-- badges: start -->
<!-- badges: end -->

`vbdata` is an R package that provides an Quarto-powered app allowing to encode data from a volleyball game score sheet and to extract the data as `.csv`.

It is aimed in future development to offer analytics solution for the data extracted with the app.

## Installation

You can install the development version of `vbdata` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("gorinsimon/vbdata")
```

## Usage

After having installed the package, you need to make sure that Quarto is installed on your machine (see [https://quarto.org/docs/get-started/](https://quarto.org/docs/get-started/)). Next, run the following command to run the app locally.

```{r example, eval=FALSE}
vbdata::run_vb_game_encoder()
```
